Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-14 automatica/paper.tex
intro

We provide experimental results showing that all our approaches are able to
efficiently synthesize safe controllers for a set of intricate physical
plant models taken from the digital control literature.

>>>>

We provide experimental results showing that both our approaches are able to
efficiently synthesize safe controllers for a set of intricate physical
plant models taken from the digital control literature.
\addtodo{add more here once we have the experimental results ready}
